### 2017-11-23 UOW_thesis_template_v2-0/thesis_template/chapters/euroComp.tex
Fixed up last corrections given by Marianito
:art: Jeff's changes before Marianito's help

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. The two auxiliary functions in~\eqref{eqn:funcs} are the ``building blocks'' for all possible financial payoffs in options pricing. For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

@@

To proceed, we assume a dividend of value proportional to the asset price is paid out on a date $t = t_d$, where $t_d$ is before the expiry. Consequently, this means that the asset price $S_t$ will decrease by a proportion of its value as it passes $t_d$. We call the proportion factor $q_d \geq 0$. Using $t_d^-$ and $t_d^+$ to indicate an infinitesimal time before and after the dividend payment date, respectively, mathematically this implies the following jump condition
	\begin{equation}
		\label{eqn:jumpcond}
		S_{t_d^+} = S_{t_d^-} - q_dS_{t_d^-} = (1-q_d)S_{t_d^-}.
	\end{equation}
A common way to price options when the underlying pays a discrete dividend is to solve the Black-Scholes equation~\eqref{eqn:blackscholes} backwards in time twice; once from expiry $T$ to $t_d^+$ and then from $t_d^-$ to an arbitrary time $t$~\cite{Wilmott1995, Jiang2005}. However, an extra step is required whereby the jump condition~\eqref{eqn:jumpcond} for $S_t$ needs to be accounted for as a boundary condition between $t_d^+$ and $t_d^-$.

@@

In this paper, we have presented an alternative technique to pricing European compound options with a general payoff. The power of this result stems from the Black-Scholes kernel, which provides us exact integral expressions for any possible financial payoff for both the compound and underlying option. The identities derived here provide a foundation to price every possible combination of vanilla compound options, and this was demonstrated extensively. Interestingly, three pseudo-put-call-parity expressions were also ascertained which highlights a unique symmetry between the standard vanilla compound options. These results also resemble the standard put-call-parity identity. Furthermore, we extended the formulas to encompass the possibility of discrete dividends. The analysis presented could be extended to accommodate for multiple discrete dividends, but the illustration with one discrete dividend already yielded favourable results. Namely for a European call-on-a-call compound option, the pricing formula for discrete dividends is extremely similar to the expression for an underlying asset possessing a continuous dividend yield. Additionally, the results are all exact. In terms of potential future research, we aim to investigate the scenario of jump-diffusion dynamics in the underlying stock and perhaps extend the generalised results to American compound options. There is also promise in analysing compound options when the SDE governing the underlying asset accounts for a discrete dividend as a fixed cash payment rather than a proportional yield. The analysis presented in this work provides a good foundation for pursuing similar pricing problems in compound options.

>>>>

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. The two auxiliary functions in~\eqref{eqn:funcs} are the building blocks for many possible financial payoffs in options pricing. For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

@@

To proceed, we assume a dividend of value proportional to the asset price is paid out on a date $t = t_d$, where $t_d$ is before the expiry. Consequently, this means that the asset price $S_t$ will decrease by a proportion of its value as it passes $t_d$. We call the proportion factor $q_d \in [0,1)$. Using $t_d^-$ and $t_d^+$ to indicate an infinitesimal time before and after the dividend payment date, respectively, mathematically this implies the following jump condition
	\begin{equation}
		\label{eqn:jumpcond}
		S_{t_d^+} = S_{t_d^-} - q_dS_{t_d^-} = (1-q_d)S_{t_d^-}.
	\end{equation}
A common way to price options when the underlying pays a discrete dividend is to solve the Black-Scholes equation~\eqref{eqn:blackscholes} backwards in time twice; once from expiry $T$ to $t_d^+$ and then from $t_d^-$ to an arbitrary time $t$~\cite{Wilmott1995, Jiang2005}. However, an extra step is required whereby the jump condition~\eqref{eqn:jumpcond} for $S_t$ needs to be accounted for as a boundary condition between $t_d^+$ and $t_d^-$.

@@

In this chapter, we have presented an alternative technique to pricing European compound options with a general payoff. The power of this result stems from the Black-Scholes kernel, which provides us exact integral expressions for any possible financial payoff for both the compound and underlying option. The identities derived here provide a foundation to price every possible combination of vanilla compound options, and this was demonstrated extensively. Interestingly, three pseudo-put-call-parity expressions were also ascertained which highlights a unique symmetry between the standard vanilla compound options. These results also resemble the standard put-call-parity identity. Furthermore, we extended the formulas to encompass the possibility of discrete dividends. The analysis presented could be extended to accommodate for multiple discrete dividends, but the illustration with one discrete dividend already yielded favourable results. Namely for a European call-on-a-call compound option, the pricing formula for discrete dividends is extremely similar to the expression for an underlying asset possessing a continuous dividend yield. Additionally, the results are all exact. In terms of potential future research, we aim to investigate the scenario of jump-diffusion dynamics in the underlying stock and perhaps extend the generalised results to American compound options. There is also promise in analysing compound options when the SDE governing the underlying asset accounts for a discrete dividend as a fixed cash payment rather than a proportional yield. The analysis presented in this work provides a good foundation for pursuing similar pricing problems in compound options.
